Fusion Moves for Correlation Clustering

### 2014-11-10 paper/egpaper_for_review.tex
refactor EHC

% Include other packages here, before hyperref.
\usepackage{my_macros}
\usepackage{paralist}
\usepackage{amsthm}
\usepackage{dirtytalk}
%\usepackage{framed}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{setspace}
%for tikz
\usepackage{tikz,pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
\usepackage{scrextend}
\usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
\usetikzlibrary{arrows,petri,topaths}
\usetikzlibrary{positioning,fit,calc}
\usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
\usetikzlibrary{calc, matrix, backgrounds}

@@

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\usepackage{bm}% ändert \boldsymbol
\def\arraystretch{0.8}
\renewcommand{\tabcolsep}{2pt}
\newcommand{\thickline}{2pt}
\newcommand{\scatterplotpath}{./scatterplots/}

@@

\section{Energy Based Hierarchical Clustering (EHC)}\label{sec:ehc}

Agglomerative hierarchical clustering (HC) is widely used
in graph / image segmentation
\cite{arbelaez_2006}.

@@

\textit{move this up} [ In each step, the edge with the highest weight $w$ is
contracted (red edges in fig. ~\ref{fig:hc_alg}).
Doing so, parallel edges edges can occur.
]

@@

\input{inputs/fig_contraction.tex}

@@

Within all experiments we used the following existing solvers 
with public available implementation.
\begin{itemize}
    \item 
    \textbf{CGC} \cite{beier_2014_cvpr} we used the public available 
    implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}.
    As reported in \cite{beier_2014_cvpr}, CGC is faster and gives better energies then \cite{yarkony_2012_eccv} and \cite{bagon_2011_arxiv}.
    Therefore we exclude those in our experiments.
    \item \textbf{KL}\cite{???}  and a public available 
        implementation \footnote{
            \label{opengm-master} 
            \url{https://github.com/opengm/opengm}
            %\label{opengm-master}
        }
    \item \textbf{MC-R,MC-I}\cite{kappes_2011_emmcvpr}  where we used a  modified 
    version of a public available implementation implementation\footref{opengm-master}.
    We replace a highly used queue with a more suitable and
    fast \emph{index-min-heap}\cite{???}.
    MC-R indicates that only the LP is solved, while MC-I solves
    the ILP.
    \item non vision solvers here TODO
\end{itemize}
And the following proposed solvers:
\begin{itemize}
\item \textbf{EHC}: Energy Based Based Hierarchical Clustering 
as described in sec.~\ref{sec:ehc}.
\item \textbf{EHC-CGC}: As CGC but warm started 
with the solution from EHC.
\end{itemize}

>>>>

% Include other packages here, before hyperref.
\usepackage{my_macros}
\usepackage{paralist}
\usepackage{amsthm}
\usepackage{dirtytalk}
%\usepackage{framed}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{setspace}
%for tikz
\usepackage{tikz,pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
%\usepackage{scrextend}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\newcommand{\footlabel}[2]{%
    \addtocounter{footnote}{1}%
    \footnotetext[\thefootnote]{%
        \addtocounter{footnote}{-1}%
        \refstepcounter{footnote}\label{#1}%
        #2%
    }%
    $^{\ref{#1}}$%
}

\newcommand{\footref}[1]{%
    $^{\ref{#1}}$%
}
\usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
\usetikzlibrary{arrows,petri,topaths}
\usetikzlibrary{positioning,fit,calc}
\usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
\usetikzlibrary{calc, matrix, backgrounds}

@@

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage{bm}% ändert \boldsymbol
\def\arraystretch{0.8}
\renewcommand{\tabcolsep}{2pt}
\newcommand{\thickline}{2pt}
\newcommand{\scatterplotpath}{./scatterplots/}

@@

\section{Energy Based Hierarchical Clustering}\label{sec:ehc}

Agglomerative hierarchical clustering (HC) is widely used
in graph / image segmentation
\cite{arbelaez_2006}.
In each step, the edge with the highest weight $w$ is
contracted (red edges in Fig.~\ref{fig:hc_alg}).
Doing so, parallel edges edges can occur.

@@

@@

\input{inputs/fig_contraction.tex}
\input{inputs/fig_projection.tex}

@@

Within all experiments we used the following existing solvers 
with public available implementation.
\begin{itemize}
    \item 
    \textbf{CGC} \cite{beier_2014_cvpr} we used the public available 
    implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}.
    As reported in \cite{beier_2014_cvpr}, CGC is faster and gives better energies then \cite{yarkony_2012_eccv} and \cite{bagon_2011_arxiv}.
    Therefore we exclude those in our experiments.
    \item \textbf{KL}\cite{???}  and a public available 
        implementation 
        \footlabel{opengm-master}{%
        %\footnote{
        %    \label{opengm-master} 
            \url{https://github.com/opengm/opengm}
            %\label{opengm-master}
        }
    \item \textbf{MC-R,MC-I}\cite{kappes_2011_emmcvpr}  where we used a  modified 
    version of a public available implementation implementation\footref{opengm-master}.
    We replace a highly used queue with a more suitable and
    fast \emph{index-min-heap}\cite{???}.
    MC-R indicates that only the LP is solved, while MC-I solves
    the ILP.
    \item non vision solvers here TODO
\end{itemize}
And the following proposed solvers:
\begin{itemize}
\item \textbf{EHC}: Energy Based Based Hierarchical Clustering 
as described in sec.~\ref{sec:ehc}.
\item \textbf{EHC-CGC}: As CGC but warm started 
with the solution from EHC.
\end{itemize}
